Multi-resolution Neural Field Estimation

### 2011-03-03 Multiresolution_framework/ltx/manuscript.tex
edits to result section

\author{In no particular order: \parham{P. Aram}, \mike{M. Dewar}, \dean{D.R. Freestone~\IEEEmembership{Graduate Student Member,~IEEE,}}, \ken{K.Scerri}, D.B. Grayden~\IEEEmembership{Member,~IEEE,} and V. Kadirkamanathan~\IEEEmembership{Member,~IEEE} % <-this % stops a space
\thanks{P. Aram* and V. Kadirkamanathan are with the Department of Automatic Control and Systems Engineering, University of Sheffield, Sheffield, S1 3JD, U.K. (e-mail:p.aram@sheffield.ac.uk; visakan@sheffield.ac.uk).}% <-this % stops a space
\thanks{D.\ R.\ Freestone and D.\ B.\ Grayden are with the Department
of Electrical and Electronic Engineering, The University of Melbourne, and The Bionic Ear Institute, VIC, Australia}
\thanks{M. Dewar is with the Department of Applied Physics and Applied Mathematics, Columbia University, New York, NY, USA}
\thanks{K. Scerri is with the Department of Systems and Control Engineering, University
of Malta, Msida, MSD 2080, Malta.}}
% <-this % stops a space
%\thanks{Manuscript received April 19, 2005; revised January 11, 2007.}}

@@

\section{Results}
To demonstrate the performance of the MRA estimation framework, data was generated synthetically  using Eqs.~\ref{eq:DiscreteTimeModel} and \ref{eq:ObservationEquation}, enabling a comparison between true and estimated parameters. 100 realizations of 1 second of data were generated where $\boldsymbol\Sigma_v=0.1 \times \mathbf{I}_{n_y}$ \dean{and the disturbance covariance was a B-spline with $j=3$.} 
The sampling period and the synaptic time constant were set to $T_s = 1$~ms and $\tau = 10$~ms, respectively. The distance between adjacent sensors was $0.5$~mm resulting into 161 observations. \parham{Since $n_x<161$ at each level, this provides enough information for state estimation due to orthogonality of the basis functions.}  The observation kernel is modeled using a B-spline function, with a width of 0.8~mm at half the maximum amplitude of the observation kernel. The spacing and bandwidth of the sensors allowed for the full spatial bandwidth of the field to be observed. The spatial cutoff frequency of the observed field, $y_t(r_n)$, was used to specify the level of decomposition required to represent the field using the wavelets. The spatial cutoff frequency was \dean{??} cycles/mm. Therefore, wavelets up to level $j=2$ (with the bandwidth $\approx[2.5,4]$ cycles/mm) can represent the significant spatial characteristics of the field. \cut{Note that wavelets due to their bandpass filter characteristics extract successively higher and higher frequency components by increasing $j$.}

Field reconstruction \dean{using the results of the EM algorithm} at different levels of approximations is shown in \figurename{\ref{fig:FieldEstimates}}. \dean{Needs more info. Like that the results are great!} The figure confirms that $j=3$ is adequate to capture the dynamics of the underlying field, where the RMSE converges to a steady value of \dean{1.04}.  The actual connectivity kernel and the decomposition is plotted in \figurename{\ref{fig:KernelEstimate}}. The reconstructed kernel is in good accordance with the actual kernel, where the actual kernel lies inside the confidence interval. The small error in the estimate is attributed to the MRA of the system used to form the estimator.
\begin{figure}[!h] 
	\centering
		\includegraphics[scale=1]{./Graph/Field.pdf}
		\caption{Actual (grey line) and estimated (black line) neural fields at a time instant for different spatial resolutions. (a) $j=0$, $n_x=17$, RMSE = 4.44. (b) $j=1$, $n_x=33$, RMSE = 1.87. (c) $j=2$, $n_x=65$, RMSE = 1.2. (d) $j=3$, $n_x=131$, RMSE = 1.04. (e) $j=4$, $n_x=263$, RMSE=1.04.}
	\label{fig:FieldEstimates}
\end{figure} 
\begin{figure}[!h] 
	\centering
		\includegraphics[scale=1]{./Graph/Kernel.pdf}
		\caption{The actual connectivity kernel is shown with the black solid line. The estimated kernel and confidence interval is shown by the red line and red shaded region ($\pm2$ std.). The 7 weighted kernel basis functions are shown by the black dashed lines.}
	\label{fig:KernelEstimate}
\end{figure}
\section{Discussion}
In this paper, we have presented a novel model-based framework for estimating cortical dynamics from electrophysiological measurements. The novel aspects include...

>>>>

\author{\parham{P. Aram}, \mike{M. Dewar}, \dean{D.R. Freestone~\IEEEmembership{Graduate Student Member,~IEEE,}}, \ken{K.Scerri}, D.B. Grayden~\IEEEmembership{Member,~IEEE,} and V. Kadirkamanathan~\IEEEmembership{Member,~IEEE} % <-this % stops a space
\thanks{P. Aram* and V. Kadirkamanathan are with the Department of Automatic Control and Systems Engineering, University of Sheffield, Sheffield, S1 3JD, U.K. (e-mail:p.aram@sheffield.ac.uk; visakan@sheffield.ac.uk).}% <-this % stops a space
\thanks{D.\ R.\ Freestone and D.\ B.\ Grayden are with the Department
of Electrical and Electronic Engineering, The University of Melbourne, and The Bionic Ear Institute, VIC, Australia}
\thanks{M. Dewar is with the Department of Applied Physics and Applied Mathematics, Columbia University, New York, NY, USA}
\thanks{K. Scerri is with the Department of Systems and Control Engineering, University
of Malta, Msida, MSD 2080, Malta.}}
% <-this % stops a space
%\thanks{Manuscript received April 19, 2005; revised January 11, 2007.}}

@@

\section{Results}
To demonstrate the performance of the MRA estimation framework, data was generated synthetically  using Eqs.~\ref{eq:DiscreteTimeModel} and \ref{eq:ObservationEquation}, enabling a comparison between true and estimated parameters. 100 realizations of 1 second of data were generated where $\boldsymbol\Sigma_v=0.1 \times \mathbf{I}_{n_y}$ \dean{and the disturbance covariance was a B-spline with $j=3$.} 
The sampling period and the synaptic time constant were set to $T_s = 1$~ms and $\tau = 10$~ms, respectively. The distance between adjacent sensors was $0.5$~mm resulting into 161 observations. \parham{Since $n_x<161$ at each level, this provides enough information for state estimation due to orthogonality of the basis functions.}  The observation kernel is modeled using a B-spline function, with a width of 0.8~mm at half the maximum amplitude of the observation kernel. The spacing and bandwidth of the sensors allowed for the full spatial bandwidth of the field to be observed. The spatial cutoff frequency of the observed field, $y_t(r_n)$, was used to specify the level of decomposition required to represent the field using the wavelets. The spatial cutoff frequency was \dean{??} cycles/mm. Therefore, wavelets up to level $j=3$ (with the bandwidth $\approx[5,8]$ cycles/mm) can represent the significant spatial characteristics of the field. \cut{Note that wavelets due to their bandpass filter characteristics extract successively higher and higher frequency components by increasing $j$.}

Field reconstruction \dean{using the results of the EM algorithm} at different levels of approximations is shown in \figurename{\ref{fig:FieldEstimates}}. \dean{Needs more info. Like that the results are great!} The figure confirms that $j=3$ is adequate to capture the dynamics of the underlying field, where the RMSE converges to a steady value of \dean{0.72}.  The actual connectivity kernel and the decomposition is plotted in \figurename{\ref{fig:KernelEstimate}}. The reconstructed kernel is in good accordance with the actual kernel, where the actual kernel lies inside the confidence interval. The small error in the estimate is attributed to the MRA of the system used to form the estimator.
\begin{figure}[!h] 
	\centering
		\includegraphics[scale=1]{./Graph/Field.pdf}
		\caption{Actual (grey line) and estimated (black line) neural fields at a time instant for different spatial resolutions. (a) $j=0$, $n_x=17$, RMSE = 2.10. (b) $j=1$, $n_x=33$, RMSE = 1.42. (c) $j=2$, $n_x=65$, RMSE = 0.80. (d) $j=3$, $n_x=131$, RMSE = 0.72. (e) $j=4$, $n_x=263$, RMSE=0.72.}
	\label{fig:FieldEstimates}
\end{figure} 
\begin{figure}[!h] 
	\centering
		\includegraphics[scale=1]{./Graph/Kernel.pdf}
		\caption{The actual connectivity kernel is shown with the black solid line. The estimated kernel and confidence interval is shown by the red line and red shaded region ($\pm2$ std.). The 7 weighted kernel basis functions are shown by the black dashed lines.}
	\label{fig:KernelEstimate}
\end{figure}
\section{Discussion}
In this paper, we have presented a novel model-based framework for estimating cortical dynamics from electrophysiological measurements. The novel aspects include...
